### 2022-08-24 manuscript.Rmd
Remove non-breaking spaces

Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s~>~`r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s~`r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`)~=~`r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$~`r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s~>~`r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s~<~`r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.

In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s~<~`r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$~`r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.

In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$~=~`r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$~=~`r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
There was no reliable difference between conditions in the P1 component, $b$~=~`r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.

In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$~=~`r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$~=~`r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$~=~`r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.

@@

In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s~>~`r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
Both clusters had a negative sign, started around 600 ms after object onset [but see @sassenhagen2019] and continued all the way until the end of the analyzed period at 1,400 ms.
They spanned a broad range of frequencies in the alpha and lower beta range as well as a broad set of channels, but appeared to be most focal at around 15 Hz and parietal channels.
Thus, semantically informed perception seems to alter not only early, evoked activity (see Event-Related Potentials above) but also later, induced activity, in the form of a reduction of post-stimulus power at parietal channels in the range of alpha and lower beta frequencies.

>>>>

Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.

In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.

In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.

In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.

@@

In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
Both clusters had a negative sign, started around 600 ms after object onset [but see @sassenhagen2019] and continued all the way until the end of the analyzed period at 1,400 ms.
They spanned a broad range of frequencies in the alpha and lower beta range as well as a broad set of channels, but appeared to be most focal at around 15 Hz and parietal channels.
Thus, semantically informed perception seems to alter not only early, evoked activity (see Event-Related Potentials above) but also later, induced activity, in the form of a reduction of post-stimulus power at parietal channels in the range of alpha and lower beta frequencies.
